Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-17 main.tex
What was wrong with obstraces?

A {\em contoured trace} is a finite or infinite sequence
$\seq{(\contour,\mach)} = (\contour_0,\mach_0),\,
(\contour_1,\mach_1),\ldots$ of (contour, machine state) pairs in which
adjacent machine states are related by $\stepstounderfull$---i.e., in which
$\mach_{i-1} \stepstounderfull \mach_i$ for each $i > 0$ in the sequence.

@@

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.

\bcp{NI is the property where:
  \begin{itemize}
  \item In each top-level pair (each element of the hyperproperty), all the
  contours coincide.
  \item If the initial machine states plus contour are variants, then the
  observervations of the two traces coincide.
  \end{itemize}
}

>>>>

A {\em contoured trace} of length $n$, where $n$ can be finite or
infinite, is a length-$n$ sequence $\seq{(\contour,\mach)}_n =
(\contour_0,\mach_0),\, (\contour_1,\mach_1),\ldots$ of (contour,
machine state) pairs in which adjacent machine states are related by
$\stepstounderfull$---i.e., in which $\mach_{i-1} \stepstounderfull
\mach_i$ for each $i > 0$ in the sequence.

@@

NI is the contoured hyperproperty where:
\begin{itemize}
\item For each pair of traces in the hyperproperty, all the contours
  coincide.
\item For each pair of traces in the hyperproperty, If the initial
  machine states plus contour are variants, then the observervations
  of the two traces coincide.
\end{itemize}

%  
% \leo{Some notes for the meeting}
%  
% In traditional NI viewed as a pair of contoured traces $\overline{(C, M_i)}$ and
% $\overline{(C, N_i)}$, we can have the following formulations:
% \begin{enumerate}
% \item $M_0, N_0 \in \mathit{Initial State}, ~\text{s.t.} ~\mathit{variant}(C, M_0, N_0)$
% \item $M_0 \in \mathit{Initial State}, N_0 \in \mathit{Variant}(C, M_0)$
% \item $M_0, N_0 \in \mathit{Reachable State}, ~\text{s.t.} ~\mathit{variant}(C, M_0, N_0)$
% \item $M_0 \in \mathit{Reachable State}, N_0 \in \mathit{Variant}(C, M_0)$
% \end{enumerate}
% %
% The (intuitive) top level property we care about is (1) - end to end
% noninterference.
% %
% Property (2) is easier to test - but not always equivalent (if the set
% of variants of an initial state can take you outside the set of
% initial states).
% %
% Property (3) is also easier to test than - you start from an arbitrary
% (reachable) state instead of an initial one, allowing to get to the
% interesting part sooner.
% %
% Property (4) corresponds to what we actually want to test - start from
% an arbitrary (reachable) state, vary it, test the trace.
%  
% As far as facilitating testing goes, the assumption of SSNI is that
% you don't need to test full traces - you can test all traces of length
% 1 and that somehow gives you confidence for the full property.
% %
% More importantly, note that going from (1,2) to (3,4) doesn't really
% change the property itself {\em as long as the contour stays identical
%   throughout the execution}.
%  
% Now, when the contour does change the expressive power of (3,4) and (1,2)
% is slightly different:
% \begin{itemize}
% \item If the contour C makes more things hidden at step $i$, then
%   starting from the (reachable) state $M_i$ and taking its variant can
%   lead to a pair $M_i, N_i$ that is not reachable from a pair of variant
%   initial states.
% \item If the contour C declassifies things at step $i$, then traces
%   that started from variants $M_0, N_0$ based on a more restrictive
%   contour C, can reach that point and no longer remain variant based
%   on the new contour.
% \end{itemize}
% Therefore an additional property of the hyperproperties when
% classification/declassification is involved, is that the traces
% in the property start at some contour level C0 and are truncated
% after C becomes more permissive than C0.
%  
% The stack property we test is just a way of testing such a
% hyperproperty more efficiently.
